\chapter*{Abstract}

This Diploma thesis deals with the augmented reality technology, which is used in a mobile application. At the moment augmented reality technology has a demand in the IT marketplace. In the future this technology will be implemented in several different mobile applications. This project is carried out in cooperation with an important industrial firm called 4relation Consulting GmbH. The latest smart phones model provides the hardware to run Augmented Reality applications. This work specifies how to use Augmented Reality with Metaio SDK for mobile Applications. Furthermore the mobile phones offer more and more graphic performance and processing power and have the potential to become a nearly ideal AR-Plattform. Even the mobile devices offers only a fraction of the processing power of a desktop pc. On the other hand they offer sufficient processing power for different tracking techniques. Moreover this thesis describes how to use a tracking system to detect an object. The aim of this project is to detect a vehicle by the tracking system. However the application of this project should detect a vehicle model and subsequently it should give an output of the information from the respective car. For the creation of a AR Application, knowledge and technologies from different parts of the information technology are required. For the tracking system , the implementation/logic of the Metaio GmbH is used. This firm offers SDK's for tracking methods , which can be integrated in mobile applications.