% Chapter9
\chapter{Resume}\label{chapter:Resume}
The project NAVAR was a great success. Not only the implementation of the project but also the improvement of our knowledge and our skills to work as a team.
\\\\
Since the start of the project we were driven to do the best we can to make a outstanding project for ourselves, our client 4relation Consulting GmbH. and our school Technische Gewerbe Museum(TGM).We improved our skills in five programming languages, which are HTML, CSS, Java , Javascript and C\#. The team acquired know how in new technologies like Windows Azure, Microsoft Dynamics Navsion and augmented reality.   
We learned to coordinate with our project team and the client. Every team member had his own responsibilities, task and deadline when something should be done or implemented. This increased our self-reliance and time management.
\\\\
Our project had also setbacks but we never lost track and continued to work eagerly. With our mental focus and the goal to succeed we were able to hit every milestone on target without delays.With the cooperation with our client we were introduced to an unknown world, the business world. 
\\\\
This unique experiences and challenges could never be achieved by typical school lessons. So we are proud and thankful that we had the opportunity to do such an amazing project. As we now look back at the start of the project we are amazed what a small group of students can create in such a short period of time.                 
\clearpage